---
title: ''
output:
  html_document:
    fig_height: 4
    fig_width: 5
    highlight: textmate
    theme: readable
  word_document: default
---

```{r, echo=FALSE, message=F, warning=F  }

#==============================================================================
#   This chunk is for every assignment: Modify line #23, then skip to line #80
#==============================================================================

  # Clear the working space
    rm(list = ls())
  
  # The following sets the path to your desired working directory:
  # Change just this command line (#24) and then skip down to line #80

    setwd("/your path/Econ42")

    
### Leave the rest of this chunk alone, unless you need to add a package
  
### Load the packages (all must have been installed)
    library(knitr)
    library(AER)
    library(sandwich)
    library(lmtest)
    library(car)
    library(stargazer)
    library(ggplot2)
    library(dplyr)
    library(gdata)
    library(compareGroups)
    library(doBy)
    library(foreign)
    library(readstata13)
    library(downloader)
    library(repmis)
    library(openintro)
    library(OIdata)
    library(reshape)
    
  ### More settings
  
  # Root directory for knitr
    opts_knit$set(root.dir = WorkDir)
  
  # turn off scientific notation except for big numbers
    options(scipen = 9)
  # set font size for qplot (default is 12)
    theme_set(theme_gray(base_size = 12))
  
  # function to calculate corrected SEs for OLS regression 
    cse <- function(reg) {
      rob = sqrt(diag(vcovHC(reg, type = "HC1")))
      return(rob)
    }
  
```

<base target="_top"/>
  
ECON 42 Lab Assignment #1

[Your name]

[Date]    

*** 
  
### Getting started with R 
  
This document is a _script_ for __R Markdown__, which you are editing with __RStudio__. When you run it, the statistical program __R__ will load the data and crunch the numbers per your instructions, and R Markdown will incorporate the results with your write-up into a single report. This means your work is 100% reproducible. To do your labs, you will edit and run scripts like this one and submit both the script and the HTML file containing the results. 

Scroll down and take a look through the whole script. Don't worry if a lot of it seems mysterious right now. 

The script contains both text and lines of R code to run the statistical analysis. The lines of R code are in blocks or "chunks" which begin and end with three single back quotes:  \```\. In your editor the R chunks can be distinguished by a light gray background. The text can be formatted in a variety of ways: _italics_, __bold__, etc. You'll see how it works when you run it.

To show a couple of examples, I have included a chunk of R code that will do the following:  

* Read data on California school districts, _caschool_, which we will use throughout ECON 41/42.  
* Create a scatter plot of average test scores against average annual per capita income, where each circle represents a school district.  
* Run two regressions and report the results in a table.  

At the beginning of the chunk you will see the option ```echo=T```. That means that the code itself will be printed in your document, along with the results. At least for now, I want you to do this in all your assignments, so I can see your code. Later in the course we can set ```ECHO=F```, which will make your homework reports much more readable. 

```{r, message=F, warning=F, comment=NA, echo=T}

#==============================================================================
#   Data section
#==============================================================================

  # Data input using read.dta (from Stock & Watson textbook site)
  caschool <- read.dta("http://wps.aw.com/wps/media/objects/11422/11696965/datasets3e/datasets/caschool.dta")
  # Read csv spreadsheet data from course github site
  acs <- read.csv("https://raw.githubusercontent.com/wsundstrom/econ42/master/data/acs_2013_data.csv")

#==============================================================================
#   Analysis section
#==============================================================================
  
  # scatter plot of test score against log of income in district
  ggplot(caschool, aes(x=avginc, y=testscr)) + 
    labs(y = "Test score", x = "Average income" , title = "CA test scores") +
    geom_point(shape=1) +           # use hollow circles
    geom_smooth(method=lm, se=F)    # add regression line

  # regressions
  reg1 <- lm(testscr ~ avginc , data = caschool)  
  reg2 <- lm(testscr ~ avginc + str , data = caschool) 
  
  # regression table
  stargazer(reg1, reg2, 
            se=list(cse(reg1), cse(reg2)),
            title="Table 1: Test score regressions", type="text", 
            column.labels=c("Simple", "Multiple"),
            df=FALSE, digits=2)

``` 
